Visualizations for article

### 2015-11-23 017-best-section-matches.Rmd
Simplify notebook generation, improve figures
Updates to analysis

---
title: "Best matches for code sections"
author: "Lincoln Mullen"
date: "September 25, 2015"
output: 
  html_document:
    keep_md: true
---

```{r message=FALSE}
library("dplyr")
library("stringr")
library("readr")
library("ggplot2")
library("RColorBrewer")
source("R/extract-date.R")
source("R/extract_code_names.R")
```

@@

```{r}
scores <- read_csv("out/scores-all-sections-pairs.csv")
scores <- scores %>% 
  rename(section_a = a, section_b = b) %>% 
  mutate(code_a = extract_code_names(section_a),
         code_b = extract_code_names(section_b),
         year_a = extract_date(code_a),
         year_b = extract_date(code_b))
scores
```

```{r}
best_section_matches <- function(code_name, scores, threshold = 0.1, top = 1) {
  require("dplyr")
  require("stringr")
  matches <- scores %>% 
    filter(code_a == code_name | code_b == code_name) %>% 
    mutate(match_code = ifelse(code_a == code_name, code_b, code_a),
           code_of_interest = ifelse(code_a == code_name, code_a, code_b),
           match_section = ifelse(code_a == code_name, section_b, section_a),
           section_of_interest = ifelse(code_a == code_name, section_a, section_b),
           match_year = ifelse(code_a == code_name, year_b, year_a)) %>% 
    filter(match_code != code_of_interest,
           match_year <= extract_date(code_name),
           similarity >= threshold) %>% 
    select(code_of_interest, section_of_interest, match_code, match_section,
           similarity, dissimilarity) %>% 
    group_by(section_of_interest) %>%
    arrange(desc(similarity)) %>% 
    top_n(top, similarity)

  all_sections <- Sys.glob(str_c("legal-codes-split/", code_name, "-0*")) %>% 
    str_replace("legal-codes-split/", "") %>% 
    str_replace("\\.txt", "")
  all <- data_frame(all_sections)

  all %>% 
    left_join(matches, by = c("all_sections" = "section_of_interest")) %>% 
    select(-code_of_interest)
} 
```

Also a function to calculate summary statistics.

```{r}
summarize_borrowings <- function(section_list) {
  section_list %>% 
    group_by(match_code) %>% 
    summarize(mean_similarity = mean(similarity),
              n = n()) %>% 
    mutate(percentage_sections = n / nrow(section_list)) %>% 
    arrange(desc(n))
}
```

@@

>>>>

---
title: "Best matches for code sections"
author: "Lincoln Mullen"
date: "September 25, 2015"
---

```{r message=FALSE}
library("dplyr")
library("stringr")
library("readr")
library("tidyr")
library("ggplot2")
library("RColorBrewer")
source("R/extract-date.R")
source("R/extract_code_names.R")
```

@@

```{r}
load("cache/lsh-sections.rda")
scores <- section_scores %>% 
  rename(section_a = a, section_b = b) %>% 
  mutate(code_a = extract_code_names(section_a),
         code_b = extract_code_names(section_b),
         year_a = extract_date(code_a),
         year_b = extract_date(code_b)) %>% 
  rename(similarity = score) %>% 
  mutate(dissimilarity = 1 - similarity)
scores
```

```{r}
source("R/summarize-borrowings.R")
source("R/best-section-matches.R")
```

@@

Heatmaps of borrowings:

```{r}
col_vector <- function(n, cols) {
  r <- trunc(n / cols)
  remainder <- n %% cols
  if (remainder > 0)
    c(rep(1:cols, r), 1:remainder)
  else
    c(rep(1:cols, r))
} 
row_vector <- function(n, cols) {
  out <- NULL
  for (i in seq_len((n / cols) + 1)) {
     out <- c(out, rep(i, cols))
  }
  out[1:n]
}
n_columns <- 40
```

Plot CA

```{r}
other <- c("MN1851", "IA1851", "KY1851", "MO1849")
best_section_matches("CA1851", scores, threshold = 0.3) %>% 
  mutate(match_code = ifelse(match_code %in% other,
                             "Other", match_code)) %>% 
  mutate(., 
         column = col_vector(nrow(.), n_columns),
         row = row_vector(nrow(.), n_columns),
         match_code = as.factor(match_code)) %>% 
  ggplot(aes(x = column, y = -row, fill = match_code, alpha)) +
  geom_tile(color = "lightgray") + 
  theme_minimal(base_size = 16) +
  coord_equal() +
  labs(x = NULL, y = NULL, title = "Borrowed sections in CA1851",
       fill = "Section borrowed from") + 
  theme(legend.position = "bottom", 
        axis.ticks = element_blank(),
        axis.line = element_blank(), axis.text = element_blank(),
        panel.background = element_blank(), panel.grid = element_blank()) +
  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
```

Plot UT1859

```{r}
other <- c("NY1848", "WI1849", "CA1850", "NY1849", "IA1851", "NY1851", "WI1856",
           "WI1858", "NY1853", "CA1851", "CA1858", "IA1859", "IN1852", "MA1858",
           "MN1851", "TN1858", "KY1851", "MA1836", "MO1856", "NE1857", "OH1853",
           "TX1855", "KS1859", "NE1859")
best_section_matches("UT1859", scores, threshold = 0.3) %>% 
  mutate(match_code = ifelse(match_code %in% other,
                             "Other", match_code)) %>% 
  mutate(., 
         column = col_vector(nrow(.), n_columns),
         row = row_vector(nrow(.), n_columns),
         match_code = as.factor(match_code)) %>% 
  ggplot(aes(x = column, y = -row, fill = match_code)) +
  geom_tile(color = "lightgray") + 
  theme_minimal(base_size = 16) +
  coord_equal() +
  labs(x = NULL, y = NULL, title = "Borrowed sections in UT1859",
       fill = "Section borrowed from") + 
  theme(legend.position = "bottom", 
        axis.ticks = element_blank(),
        axis.line = element_blank(), axis.text = element_blank(),
        panel.background = element_blank(), panel.grid = element_blank()) +
  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
```

Plot WA1855

```{r}
white_list <- c("CA1850", "NY1850", "WI1849", "CA1851", "OR1854", "IN1852")
other_maker <- function(x, white_list) {
  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
}
best_section_matches("WA1855", scores, threshold = 0.3) %>% 
  mutate(match_code = other_maker(match_code, white_list)) %>% 
  mutate(., 
         column = col_vector(nrow(.), n_columns),
         row = row_vector(nrow(.), n_columns),
         match_code = as.factor(match_code)) %>% 
  ggplot(aes(x = column, y = -row, fill = match_code)) +
  geom_tile(color = "lightgray") + 
  theme_minimal(base_size = 16) +
  coord_equal() +
  labs(x = NULL, y = NULL, title = "Borrowed sections in WA1855",
       fill = "Section borrowed from") + 
  theme(legend.position = "bottom", 
        axis.ticks = element_blank(),
        axis.line = element_blank(), axis.text = element_blank(),
        panel.background = element_blank(), panel.grid = element_blank()) +
  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
```

OR 1854

```{r}
white_list <- c("CA1850", "NY1853", "NY1851", "WI1849", "MN1851", "NY1850", "CA1851")
other_maker <- function(x, white_list) {
  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
}
best_section_matches("OR1854", scores, threshold = 0.15) %>% 
  mutate(match_code = other_maker(match_code, white_list)) %>% 
  mutate(., 
         column = col_vector(nrow(.), n_columns),
         row = row_vector(nrow(.), n_columns),
         match_code = as.factor(match_code)) %>% 
  ggplot(aes(x = column, y = -row, fill = match_code)) +
  geom_tile(color = "lightgray") + 
  theme_minimal(base_size = 16) +
  coord_equal() +
  labs(x = NULL, y = NULL, title = "Borrowed sections in OR1854",
       fill = "Section borrowed from") + 
  theme(legend.position = "bottom", 
        axis.ticks = element_blank(),
        axis.line = element_blank(), axis.text = element_blank(),
        panel.background = element_blank(), panel.grid = element_blank()) +
  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
```

NC1868

```{r}
white_list <- c("DT1668", "NY1851", "NY1849", "NY1850", "WI1858", "WI1856")
other_maker <- function(x, white_list) {
  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
}
best_section_matches("NC1868", scores, threshold = 0.3) %>% 
  mutate(match_code = other_maker(match_code, white_list)) %>% 
  mutate(., 
         column = col_vector(nrow(.), n_columns),
         row = row_vector(nrow(.), n_columns),
         match_code = as.factor(match_code)) %>% 
  ggplot(aes(x = column, y = -row, fill = match_code)) +
  geom_tile(color = "lightgray") + 
  theme_minimal(base_size = 16) +
  coord_equal() +
  labs(x = NULL, y = NULL, title = "Borrowed sections in NC1868",
       fill = "Section borrowed from") + 
  theme(legend.position = "bottom", 
        axis.ticks = element_blank(),
        axis.line = element_blank(), axis.text = element_blank(),
        panel.background = element_blank(), panel.grid = element_blank()) +
  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
```

IA1859

```{r}
white_list <- c("IA1851", "NE1857", "KY1854")
other_maker <- function(x, white_list) {
  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
}
best_section_matches("IA1859", scores, threshold = 0.3) %>% 
  mutate(match_code = other_maker(match_code, white_list)) %>% 
  mutate(., 
         column = col_vector(nrow(.), n_columns),
         row = row_vector(nrow(.), n_columns),
         match_code = as.factor(match_code)) %>% 
  ggplot(aes(x = column, y = -row, fill = match_code)) +
  geom_tile(color = "lightgray") + 
  theme_minimal(base_size = 16) +
  coord_equal() +
  labs(x = NULL, y = NULL, title = "Borrowed sections in IA1859",
       fill = "Section borrowed from") + 
  theme(legend.position = "bottom", 
        axis.ticks = element_blank(),
        axis.line = element_blank(), axis.text = element_blank(),
        panel.background = element_blank(), panel.grid = element_blank()) +
  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
```

NM1897

```{r}
white_list <- c("MO", "NM", "IA", "NY", "MN", "WI")
other_maker <- function(x, white_list) {
  ifelse(is.na(x), NA, ifelse(x %in% white_list, x, "Other"))
}
best_section_matches("NM1897", scores, threshold = 0.15) %>% 
  mutate(match_state = str_sub(match_code, start = 1, end = 2)) %>% 
  mutate(match_state = other_maker(match_state, white_list)) %>% 
  mutate(., 
         column = col_vector(nrow(.), n_columns),
         row = row_vector(nrow(.), n_columns),
         match_code = as.factor(match_code)) %>% 
  ggplot(aes(x = column, y = -row, fill = match_state)) +
  geom_tile(color = "lightgray") + 
  theme_minimal(base_size = 16) +
  coord_equal() +
  labs(x = NULL, y = NULL, title = "Borrowed sections in NM1897",
       fill = "Section borrowed from") + 
  theme(legend.position = "bottom", 
        axis.ticks = element_blank(),
        axis.line = element_blank(), axis.text = element_blank(),
        panel.background = element_blank(), panel.grid = element_blank()) +
  scale_fill_brewer(type = "qual", na.value = "gray", palette = 6)
```

Summarize by state

```{r}
summarize_by_state <- function(section_list) {
  section_list %>% 
    mutate(match_state = str_sub(match_code, start = 1, end = 2)) %>% 
    group_by(match_state) %>% 
    summarize(original_code = unique(original_code),
              mean_similarity = mean(similarity),
              n = n()) %>% 
    mutate(percentage_sections = n / nrow(section_list)) %>% 
    arrange(desc(n)) %>% 
    select(original_code, match_state, mean_similarity, n, percentage_sections)
}
```

### 2015-11-23 022-visualizations-for-article.Rmd
Updates to analysis

```{r}
CA1851 <- best_section_matches("CA1851", borrowings, threshold = 0.2)
CA1851
summarize_borrowings(CA1851)
```

@@

```{r}
section_pct <- codes %>% 
  mclapply(best_section_matches, scores = borrowings, threshold = 0.2)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
section_pct
```

@@

```{r}
# Note that original code is a misnomer here
edges <- section_pct %>% 
  mutate(original_date = extract_date(original_code),
         match_date = extract_date(match_code)) %>% 
  filter(percentage_sections >= 0.05,
         !is.na(match_code),
         original_code >= match_code) %>% 
  select(original_code, match_code, weight = percentage_sections)
edges
```

@@

```{r}
g <- graph_from_data_frame(edges, directed = TRUE)
set.seed(4821)
l <- layout.fruchterman.reingold(g, weights = E(g)$weight)
par(mar = c(0,0,1,0))
plot(g, edge.width = E(g)$weight * 8, layout = l,
     edge.arrow.size = 0.65, vertex.size = 5)
title("Codes of Civil Procedure by percentage of sections")
```

>>>>

```{r}
CA1851 <- best_section_matches("CA1851", borrowings, threshold = 0.15)
CA1851
summarize_borrowings(CA1851)
```

@@

```{r}
section_pct <- codes %>% 
  mclapply(best_section_matches, scores = borrowings, threshold = 0.15)  %>% 
  mclapply(summarize_borrowings) %>% 
  bind_rows()
section_pct
```

@@

```{r}
# Note that original code is a misnomer here
edges <-
  section_pct %>% 
  mutate(original_date = extract_date(original_code),
         match_date = extract_date(match_code)) %>% 
  filter(percentage_sections >= 0.05,
         !is.na(match_code),
         original_date >= match_date) %>% 
  select(original_code, match_code, weight = percentage_sections) %>% 
  group_by(original_code) %>% 
  top_n(2, weight)
edges
```

@@

```{r}
g <- graph_from_data_frame(edges, directed = TRUE) 
nodes <- distances(g, to = "NY1850", algorithm = "unweighted") %>% as.data.frame() %>% 
  add_rownames() %>% 
  rename(name = rowname, distance = NY1850) %>% 
  mutate(color = ifelse(distance == 0, "red",
                        ifelse(distance == 1, "green",
                               ifelse(distance == 2, "yellow", "lightblue"))))

nodes[nodes$name == "NY1848", "color"] <- "red"
nodes[nodes$name == "NY1849", "color"] <- "red"
nodes[nodes$name == "NY1850", "color"] <- "red"
nodes[nodes$name == "NY1851", "color"] <- "red"
g <- graph_from_data_frame(edges, directed = TRUE, vertices = nodes) 
V(g)$year <- V(g)$name %>% extract_date()
set.seed(4221)

# g <- g %>% decompose() %>% `[[`(1)

g <- add_layout_(g, with_graphopt(niter = 4000, spring.length = 25), normalize())

plot_before_year <- function(x, year) {
  x_before <- induced.subgraph(x, which(V(x)$year <= year))
  n <- V(x)$name
  n_before <- V(x_before)$name
  filter <- n %in% n_before
  x_before$layout <- x_before$layout[filter, ]
  par(mar = c(0,0,1,0))
  plot(x_before, edge.width = E(x_before)$weight * 8,
       edge.arrow.size = 0.0, vertex.size = 5)
  title(paste0("Codes of Civil Procedure before ", year))
}

for (i in seq(1850, 1900, 5)) {
  png(filename = paste0("out/field-code-network-ALL", i, ".png"), width = 1200,
      height = 900)
  plot_before_year(g, i)
  dev.off()
}
```
